\section{Survey}

\subsection{Introductory text}

\subsubsection{Page 1}
In this survey, you will be ask you about five hypothetical scientific experiments. For each, we will ask you to:
\begin{itemize}
\item \textit{Carefully} read an abstract description of the experiment (350 words or fewer).
\item Answer 4 multiple-choice questions about each experiment.
\item Optionally provide short explanations of your answers.
\end{itemize}
Finally, we will ask you some brief demographic questions at the end of the study. All personal information (e.g., age) is optional. Your responses will be kept anonymous, though we reserve the right to copy or quote the responses you provide.

The entire survey should take under 10 minutes of your time and pays \$1.00.

This survey is part of a research project being conducted by the The Ethical Research Project.

If you have any questions, please feel free to contact us at: team@ethicalresearch.org.

\subsubsection{Page 2}
Each of the following five pages will contain a description of a hypothetical scientific experiment, followed by questions about that experiment. In order to answer the questions, please read the description of each experiment carefully.

\subsection{Questions for each scenario}

\noindent
If someone you cared about were a candidate participant for this experiment, would you want that person to be included as a participant?
\\
\{Yes; I have no preference; No\}
\\
\\
Please explain your answer.

\noindent
Do you believe the researchers should be allowed to proceed with this experiment?
\\
\{Yes; Yes, but with caution; I'm not sure; No\}
\\
\\
Please explain your answer. (optional)

\noindent
Are you aware of having ever participated in such a study?
\{Yes;  No\}
\\
{[}If `Yes'{]}
Please tell us approximately when and where (if in person) you participated in this study:

\noindent
Are you aware of a study like this one having been performed by researchers in the past? (For example, have you have heard about it in the news or learned about it in a class?)
\{Yes;  No\}
\\
{[}If `Yes'{]} Please explain how you learned about this study.

\subsection{Final questions}

\noindent
In what year were you born? (please use a four-digit year, or 'd' if you decline to answer)

\noindent
What is your gender?
\\
\{Male;Female;I'm uncomfortable answering\}

\noindent
What is your occupation?

\noindent
Have you ever purchased goods advertised via an unsolicited marketing email?
\\
\{Yes;No;I'm uncomfortable answering\}

\noindent
Have you ever participated in a study that involved deception?
\\
\{Yes; No; I'm uncomfortable answering\}
\\
Please explain.

\noindent
Prior to participating in this study, had you heard about Facebook's ‘mood’ study (the experiment that has the subject in many recent news stories).
\\
\{Yes; No\}